---
title: "Forest Plots - Cognitive Progression Groups"
author: "Yihan Wang"
date: "2025-09-16"
output:
  word_document: default
  pdf_document: default
---

1. PROGRESSION GROUPS (4 groups):
   Groups included:
   - Non-progression (CU stable + MCI stable combined)
   - CU-MCI progression (progression from CU to MCI)
   - CU/MCI-AD progression (progression to AD dementia)
   - AD (dementia patients)

2. COMORBIDITY ADJUSTMENTS:
   Added to ALL models as covariates:
   - CVD (Cardiovascular disease)
   - Endocrine (Endocrine disorders including diabetes)
   - Psychiatric (Psychiatric conditions)
   
3. MEDICATION × TIME INTERACTIONS:
   All 7 medications include interaction with year_since_baseline:
   - ACEi × Time, ARB × Time, β-Blocker × Time, CCB × Time
   - Diuretic × Time, Metformin × Time, Statin × Time
   
   This allows assessment of whether medication effects change over follow-up period.

4. MODEL FORMULA STRUCTURE:
   CDR ~ year_since_baseline + 
         age + sex + edu + APOE4 + 
         CVD + Endocrine + Psychiatric +
         ACEi + ARB + BetaBlk + CCB + Diuretic + Metformin + Statin + 
         drug:year_since_baseline (for all 7 drugs) +
         (1 + year_since_baseline | id)

```{r}
rm(list=ls())
library(missRanger)
library(dplyr)
library(lubridate)
library(lme4)       # mixed models
library(lmerTest)   # p-values for lmer
library(splines)
library(conflicted)
library(broom.mixed)
library(dplyr)
library(stringr)
library(forcats)
library(ggplot2)
library(forestploter)
library(grid)
library(gridtext)
conflicts_prefer(dplyr::lag)
conflicts_prefer(lmerTest::lmer)
conflicts_prefer(dplyr::filter)
```

```{r}
source("medication-lmer-utility.R")
source("plots.R")
```

```{r}
NACC_full_df_cdr<-read.csv("../preprocessed_data/NACC/NACC_cdr_imputed_binary.csv")
AIBL_full_df_cdr<-read.csv("../preprocessed_data/AIBL/AIBL_cdr_imputed_binary.csv")
HABS_full_df_cdr<-read.csv("../preprocessed_data/HABSHD/HABSHD_cdr_imputed_binary.csv")
NACC_full_df_cdr$edu <- scale(NACC_full_df_cdr$edu)
NACC_full_df_cdr$age <- scale(NACC_full_df_cdr$age)
AIBL_full_df_cdr$edu <- scale(AIBL_full_df_cdr$edu)
AIBL_full_df_cdr$age <- scale(AIBL_full_df_cdr$age)
HABS_full_df_cdr$edu <- scale(HABS_full_df_cdr$edu)
HABS_full_df_cdr$age <- scale(HABS_full_df_cdr$age)
```

```{r}
# Split by progression groups
NACC_split <- split_by_progression(NACC_full_df_cdr, id_col = "id", visit_col = "visit_no", status_col = "status")
AIBL_split <- split_by_progression(AIBL_full_df_cdr, id_col = "id", visit_col = "visit_no", status_col = "status")
HABS_split <- split_by_progression(HABS_full_df_cdr, id_col = "id", visit_col = "visit_no", status_col = "status")

# Extract groups (function now directly returns the 4 groups we need)
# Non-progression (stable CU + stable MCI combined by the function)
NACC_non_prog = NACC_split$groups$Non_progression
AIBL_non_prog = AIBL_split$groups$Non_progression
HABS_non_prog = HABS_split$groups$Non_progression

# CU-MCI progression
NACC_cu_mci_prog = NACC_split$groups$CU_MCI_progression
AIBL_cu_mci_prog = AIBL_split$groups$CU_MCI_progression
HABS_cu_mci_prog = HABS_split$groups$CU_MCI_progression

# CU/MCI-AD progression
NACC_to_ad_prog = NACC_split$groups$CU_MCI_AD_progression
AIBL_to_ad_prog = AIBL_split$groups$CU_MCI_AD_progression
HABS_to_ad_prog = HABS_split$groups$CU_MCI_AD_progression

# AD
NACC_ad = NACC_split$groups$AD_stable
AIBL_ad = AIBL_split$groups$AD_stable
HABS_ad = HABS_split$groups$AD_stable
```
# Full

```{r}
NACC_full_df_cdr$visit_date <- as.Date(NACC_full_df_cdr$visit_date, format = "%Y-%m-%d")
fit_full_NACC <- lmer(
  CDR ~ year_since_baseline +
    age + sex + edu + APOE4 +
    CVD + Endocrine + Psychiatric +
    ACEi + ARB + BetaBlk + CCB + Diuretic + Metformin + Statin + 
    ACEi:year_since_baseline + ARB:year_since_baseline + BetaBlk:year_since_baseline +
    CCB:year_since_baseline + Diuretic:year_since_baseline + 
    Metformin:year_since_baseline + Statin:year_since_baseline +
    (1 + year_since_baseline | id),
  data = NACC_full_df_cdr
)
summary(fit_full_NACC)
```

```{r}
AIBL_full_df_cdr$visit_date <- as.Date(AIBL_full_df_cdr$visit_date, format = "%Y-%m-%d")
fit_full_AIBL <- lmer(
  CDR ~ year_since_baseline +
    age + sex + edu + APOE4 +
    CVD + Endocrine + Psychiatric +
    ACEi + ARB + BetaBlk + CCB + Diuretic + Metformin + Statin + 
    ACEi:year_since_baseline + ARB:year_since_baseline + BetaBlk:year_since_baseline +
    CCB:year_since_baseline + Diuretic:year_since_baseline + 
    Metformin:year_since_baseline + Statin:year_since_baseline +
    (1 + year_since_baseline | id),
  data = AIBL_full_df_cdr
)
summary(fit_full_AIBL)
```

```{r}
HABS_full_df_cdr$visit_date <- as.Date(HABS_full_df_cdr$visit_date, format = "%Y-%m-%d")
fit_full_HABS <- lmer(
  CDR ~ year_since_baseline +
    age + sex + edu + APOE4 +
    CVD + Endocrine + Psychiatric +
    ACEi + ARB + BetaBlk + CCB + Diuretic + Metformin + Statin + 
    ACEi:year_since_baseline + ARB:year_since_baseline + BetaBlk:year_since_baseline +
    CCB:year_since_baseline + Diuretic:year_since_baseline + 
    Metformin:year_since_baseline + Statin:year_since_baseline +
    (1 + year_since_baseline | id),
  data = HABS_full_df_cdr
)
summary(fit_full_HABS)
```


# Non-progression (CU + MCI stable combined)

```{r}
NACC_non_prog$visit_date <- as.Date(NACC_non_prog$visit_date, format = "%Y-%m-%d")
fit_NACC_NON_PROG <- lmer(
  CDR ~ year_since_baseline +
    age + sex + edu + APOE4 +
    CVD + Endocrine + Psychiatric +
    ACEi + ARB + BetaBlk + CCB + Diuretic + Metformin + Statin + 
    ACEi:year_since_baseline + ARB:year_since_baseline + BetaBlk:year_since_baseline +
    CCB:year_since_baseline + Diuretic:year_since_baseline + 
    Metformin:year_since_baseline + Statin:year_since_baseline +
    (1 + year_since_baseline | id),
  data = NACC_non_prog
)
summary(fit_NACC_NON_PROG)

# BH-adjusted p-values
coef_summary <- coef(summary(fit_NACC_NON_PROG))
p_values <- coef_summary[, "Pr(>|t|)"]
p_adjusted <- p.adjust(p_values, method = "BH")
cat("nBH-adjusted p-values:n")
print(data.frame(Term = rownames(coef_summary), P.value = p_values, P.adjusted = p_adjusted))
```

```{r}
AIBL_non_prog$visit_date <- as.Date(AIBL_non_prog$visit_date, format = "%Y-%m-%d")
fit_AIBL_NON_PROG <- lmer(
  CDR ~ year_since_baseline +
    age + sex + edu + APOE4 +
    CVD + Endocrine + Psychiatric +
    ACEi + ARB + BetaBlk + CCB + Diuretic + Metformin + Statin + 
    ACEi:year_since_baseline + ARB:year_since_baseline + BetaBlk:year_since_baseline +
    CCB:year_since_baseline + Diuretic:year_since_baseline + 
    Metformin:year_since_baseline + Statin:year_since_baseline +
    (1 + year_since_baseline | id),
  data = AIBL_non_prog
)
summary(fit_AIBL_NON_PROG)

# BH-adjusted p-values
coef_summary <- coef(summary(fit_AIBL_NON_PROG))
p_values <- coef_summary[, "Pr(>|t|)"]
p_adjusted <- p.adjust(p_values, method = "BH")
cat("nBH-adjusted p-values:n")
print(data.frame(Term = rownames(coef_summary), P.value = p_values, P.adjusted = p_adjusted))
```

```{r}
HABS_non_prog$visit_date <- as.Date(HABS_non_prog$visit_date, format = "%Y-%m-%d")
fit_HABS_NON_PROG <- lmer(
  CDR ~ year_since_baseline +
    age + sex + edu + APOE4 +
    CVD + Endocrine + Psychiatric +
    ACEi + ARB + BetaBlk + CCB + Diuretic + Metformin + Statin + 
    ACEi:year_since_baseline + ARB:year_since_baseline + BetaBlk:year_since_baseline +
    CCB:year_since_baseline + Diuretic:year_since_baseline + 
    Metformin:year_since_baseline + Statin:year_since_baseline +
    (1 + year_since_baseline | id),
  data = HABS_non_prog
)
summary(fit_HABS_NON_PROG)

# BH-adjusted p-values
coef_summary <- coef(summary(fit_HABS_NON_PROG))
p_values <- coef_summary[, "Pr(>|t|)"]
p_adjusted <- p.adjust(p_values, method = "BH")
cat("nBH-adjusted p-values:n")
print(data.frame(Term = rownames(coef_summary), P.value = p_values, P.adjusted = p_adjusted))
```

# CU-MCI Progression

```{r}
NACC_cu_mci_prog$visit_date <- as.Date(NACC_cu_mci_prog$visit_date, format = "%Y-%m-%d")
fit_NACC_CU_MCI_PROG <- lmer(
  CDR ~ year_since_baseline +
    age + sex + edu + APOE4 +
    CVD + Endocrine + Psychiatric +
    ACEi + ARB + BetaBlk + CCB + Diuretic + Metformin + Statin + 
    ACEi:year_since_baseline + ARB:year_since_baseline + BetaBlk:year_since_baseline +
    CCB:year_since_baseline + Diuretic:year_since_baseline + 
    Metformin:year_since_baseline + Statin:year_since_baseline +
    (1 + year_since_baseline | id),
  data = NACC_cu_mci_prog
)
summary(fit_NACC_CU_MCI_PROG)

# BH-adjusted p-values
coef_summary <- coef(summary(fit_NACC_CU_MCI_PROG))
p_values <- coef_summary[, "Pr(>|t|)"]
p_adjusted <- p.adjust(p_values, method = "BH")
cat("nBH-adjusted p-values:n")
print(data.frame(Term = rownames(coef_summary), P.value = p_values, P.adjusted = p_adjusted))
```

```{r}
AIBL_cu_mci_prog$visit_date <- as.Date(AIBL_cu_mci_prog$visit_date, format = "%Y-%m-%d")
fit_AIBL_CU_MCI_PROG <- lmer(
  CDR ~ year_since_baseline +
    age + sex + edu + APOE4 +
    CVD + Endocrine + Psychiatric +
    ACEi + ARB + BetaBlk + CCB + Diuretic + Metformin + Statin + 
    ACEi:year_since_baseline + ARB:year_since_baseline + BetaBlk:year_since_baseline +
    CCB:year_since_baseline + Diuretic:year_since_baseline + 
    Metformin:year_since_baseline + Statin:year_since_baseline +
    (1 + year_since_baseline | id),
  data = AIBL_cu_mci_prog
)
summary(fit_AIBL_CU_MCI_PROG)

# BH-adjusted p-values
coef_summary <- coef(summary(fit_AIBL_CU_MCI_PROG))
p_values <- coef_summary[, "Pr(>|t|)"]
p_adjusted <- p.adjust(p_values, method = "BH")
cat("nBH-adjusted p-values:n")
print(data.frame(Term = rownames(coef_summary), P.value = p_values, P.adjusted = p_adjusted))
```

```{r}
HABS_cu_mci_prog$visit_date <- as.Date(HABS_cu_mci_prog$visit_date, format = "%Y-%m-%d")
fit_HABS_CU_MCI_PROG <- lmer(
  CDR ~ year_since_baseline +
    age + sex + edu + APOE4 +
    CVD + Endocrine + Psychiatric +
    ACEi + ARB + BetaBlk + CCB + Diuretic + Metformin + Statin + 
    ACEi:year_since_baseline + ARB:year_since_baseline + BetaBlk:year_since_baseline +
    CCB:year_since_baseline + Diuretic:year_since_baseline + 
    Metformin:year_since_baseline + Statin:year_since_baseline +
    (1 + year_since_baseline | id),
  data = HABS_cu_mci_prog
)
summary(fit_HABS_CU_MCI_PROG)

# BH-adjusted p-values
coef_summary <- coef(summary(fit_HABS_CU_MCI_PROG))
p_values <- coef_summary[, "Pr(>|t|)"]
p_adjusted <- p.adjust(p_values, method = "BH")
cat("nBH-adjusted p-values:n")
print(data.frame(Term = rownames(coef_summary), P.value = p_values, P.adjusted = p_adjusted))
```

# CU/MCI-AD Progression

```{r}
NACC_to_ad_prog$visit_date <- as.Date(NACC_to_ad_prog$visit_date, format = "%Y-%m-%d")
fit_NACC_TO_AD_PROG <- lmer(
  CDR ~ year_since_baseline +
    age + sex + edu + APOE4 +
    CVD + Endocrine + Psychiatric +
    ACEi + ARB + BetaBlk + CCB + Diuretic + Metformin + Statin + 
    ACEi:year_since_baseline + ARB:year_since_baseline + BetaBlk:year_since_baseline +
    CCB:year_since_baseline + Diuretic:year_since_baseline + 
    Metformin:year_since_baseline + Statin:year_since_baseline +
    (1 + year_since_baseline | id),
  data = NACC_to_ad_prog
)
summary(fit_NACC_TO_AD_PROG)

# BH-adjusted p-values
coef_summary <- coef(summary(fit_NACC_TO_AD_PROG))
p_values <- coef_summary[, "Pr(>|t|)"]
p_adjusted <- p.adjust(p_values, method = "BH")
cat("nBH-adjusted p-values:n")
print(data.frame(Term = rownames(coef_summary), P.value = p_values, P.adjusted = p_adjusted))
```

```{r}
AIBL_to_ad_prog$visit_date <- as.Date(AIBL_to_ad_prog$visit_date, format = "%Y-%m-%d")
fit_AIBL_TO_AD_PROG <- lmer(
  CDR ~ year_since_baseline +
    age + sex + edu + APOE4 +
    CVD + Endocrine + Psychiatric +
    ACEi + ARB + BetaBlk + CCB + Diuretic + Metformin + Statin + 
    ACEi:year_since_baseline + ARB:year_since_baseline + BetaBlk:year_since_baseline +
    CCB:year_since_baseline + Diuretic:year_since_baseline + 
    Metformin:year_since_baseline + Statin:year_since_baseline +
    (1 + year_since_baseline | id),
  data = AIBL_to_ad_prog
)
summary(fit_AIBL_TO_AD_PROG)

# BH-adjusted p-values
coef_summary <- coef(summary(fit_AIBL_TO_AD_PROG))
p_values <- coef_summary[, "Pr(>|t|)"]
p_adjusted <- p.adjust(p_values, method = "BH")
cat("nBH-adjusted p-values:n")
print(data.frame(Term = rownames(coef_summary), P.value = p_values, P.adjusted = p_adjusted))
```

```{r}
HABS_to_ad_prog$visit_date <- as.Date(HABS_to_ad_prog$visit_date, format = "%Y-%m-%d")
fit_HABS_TO_AD_PROG <- lmer(
  CDR ~ year_since_baseline +
    age + sex + edu + APOE4 +
    CVD + Endocrine + Psychiatric +
    ACEi + ARB + BetaBlk + CCB + Diuretic + Metformin + Statin + 
    ACEi:year_since_baseline + ARB:year_since_baseline + BetaBlk:year_since_baseline +
    CCB:year_since_baseline + Diuretic:year_since_baseline + 
    Metformin:year_since_baseline + Statin:year_since_baseline +
    (1 + year_since_baseline | id),
  data = HABS_to_ad_prog
)
summary(fit_HABS_TO_AD_PROG)

# BH-adjusted p-values
coef_summary <- coef(summary(fit_HABS_TO_AD_PROG))
p_values <- coef_summary[, "Pr(>|t|)"]
p_adjusted <- p.adjust(p_values, method = "BH")
cat("nBH-adjusted p-values:n")
print(data.frame(Term = rownames(coef_summary), P.value = p_values, P.adjusted = p_adjusted))
```

# AD

```{r}
NACC_ad$visit_date <- as.Date(NACC_ad$visit_date, format = "%Y-%m-%d")
fit_NACC_AD <- lmer(
  CDR ~ year_since_baseline +
    age + sex + edu + APOE4 +
    CVD + Endocrine + Psychiatric +
    ACEi + ARB + BetaBlk + CCB + Diuretic + Metformin + Statin + 
    ACEi:year_since_baseline + ARB:year_since_baseline + BetaBlk:year_since_baseline +
    CCB:year_since_baseline + Diuretic:year_since_baseline + 
    Metformin:year_since_baseline + Statin:year_since_baseline +
    (1 + year_since_baseline | id),
  data = NACC_ad
)
summary(fit_NACC_AD)

# BH-adjusted p-values
coef_summary <- coef(summary(fit_NACC_AD))
p_values <- coef_summary[, "Pr(>|t|)"]
p_adjusted <- p.adjust(p_values, method = "BH")
cat("nBH-adjusted p-values:n")
print(data.frame(Term = rownames(coef_summary), P.value = p_values, P.adjusted = p_adjusted))
```

```{r}
AIBL_ad$visit_date <- as.Date(AIBL_ad$visit_date, format = "%Y-%m-%d")
fit_AIBL_AD <- lmer(
  CDR ~ year_since_baseline +
    age + sex + edu + APOE4 +
    CVD + Endocrine + Psychiatric +
    ACEi + ARB + BetaBlk + CCB + Diuretic + Metformin + Statin + 
    ACEi:year_since_baseline + ARB:year_since_baseline + BetaBlk:year_since_baseline +
    CCB:year_since_baseline + Diuretic:year_since_baseline + 
    Metformin:year_since_baseline + Statin:year_since_baseline +
    (1 + year_since_baseline | id),
  data = AIBL_ad
)
summary(fit_AIBL_AD)

# BH-adjusted p-values
coef_summary <- coef(summary(fit_AIBL_AD))
p_values <- coef_summary[, "Pr(>|t|)"]
p_adjusted <- p.adjust(p_values, method = "BH")
cat("nBH-adjusted p-values:n")
print(data.frame(Term = rownames(coef_summary), P.value = p_values, P.adjusted = p_adjusted))
```

```{r}
HABS_ad$visit_date <- as.Date(HABS_ad$visit_date, format = "%Y-%m-%d")
fit_HABS_AD <- lmer(
  CDR ~ year_since_baseline +
    age + sex + edu + APOE4 +
    CVD + Endocrine + Psychiatric +
    ACEi + ARB + BetaBlk + CCB + Diuretic + Metformin + Statin + 
    ACEi:year_since_baseline + ARB:year_since_baseline + BetaBlk:year_since_baseline +
    CCB:year_since_baseline + Diuretic:year_since_baseline + 
    Metformin:year_since_baseline + Statin:year_since_baseline +
    (1 + year_since_baseline | id),
  data = HABS_ad
)
summary(fit_HABS_AD)

# BH-adjusted p-values
coef_summary <- coef(summary(fit_HABS_AD))
p_values <- coef_summary[, "Pr(>|t|)"]
p_adjusted <- p.adjust(p_values, method = "BH")
cat("nBH-adjusted p-values:n")
print(data.frame(Term = rownames(coef_summary), P.value = p_values, P.adjusted = p_adjusted))
```


# plots
```{r}
terms_all <-c(
    "year_since_baseline","age","sex","edu","APOE4",
    "CVD", "Endocrine", "Psychiatric",
    "ACEi","ARB","BetaBlk","CCB",
    "Diuretic","Metformin", "Statin",
    "year_since_baseline:ACEi","year_since_baseline:ARB",
    "year_since_baseline:BetaBlk","year_since_baseline:CCB",
    "year_since_baseline:Diuretic", "year_since_baseline:Metformin",
    "year_since_baseline:Statin"
  )
terms_rename <- c(
    "year_since_baseline"="Time",
    "age"="Age (baseline)",
    "sex"="Sex (ref: Male)",
    "edu"="Education (z-scored)",
    "APOE4"="APOE4 carrier (ref: No)",
    "CVD"="CVD",
    "Endocrine"="Endocrine disease",
    "Psychiatric"="Psychiatric disease",
    "ACEi"="ACEi",
    "ARB"="ARBs",
    "BetaBlk"="β-Blocker",
    "CCB"="CCBs",
    "Diuretic"="Diuretics",
    "Metformin"="Metformin",
    "Statin"="Statins",
    "year_since_baseline:ACEi"="ACEi × Time",
    "year_since_baseline:ARB"="ARBs × Time",
    "year_since_baseline:BetaBlk"="β-Blocker × Time",
    "year_since_baseline:CCB"="CCBs × Time",
    "year_since_baseline:Diuretic"="Diuretics × Time",
    "year_since_baseline:Metformin"="Metformin × Time",
    "year_since_baseline:Statin"="Statins × Time"
  )
```


```{r}
dt_cog = make_dt_from_fits(
  fits = list(
    `Overall` = list(fit_full_NACC, fit_full_AIBL, fit_full_HABS),
    `Non-progression`     = list(fit_NACC_NON_PROG,   fit_AIBL_NON_PROG,   fit_HABS_NON_PROG),
    `CU-MCI progression`   = list(fit_NACC_CU_MCI_PROG,   fit_AIBL_CU_MCI_PROG,   fit_HABS_CU_MCI_PROG),
    `CU/MCI-ADem progression`     = list(fit_NACC_TO_AD_PROG,   fit_AIBL_TO_AD_PROG,   fit_HABS_TO_AD_PROG),
    `ADem-stable`   = list(fit_NACC_AD,   fit_AIBL_AD,   fit_HABS_AD)
  ),
  term= terms_all,
  cohorts = c("NACC","AIBL","HABS"),
  term_labels  = terms_rename,
  method = "REML",
  digits = 3,
  p_adjust = "none"
)
```


```{r}
png_path <- "../plots/forestplot/Figure 2.png"
dir.create(dirname(png_path), recursive = TRUE, showWarnings = FALSE)

# Expanded width to 15 in for a wider landscape layout (5 parallel group tracks)
img_w <- 15; img_h <- 10; img_dpi <- 500

if (requireNamespace("ragg", quietly = TRUE)){
  ragg::agg_png(png_path, width = img_w, height = img_h,
                units = "in", res = img_dpi, background = "white")
} else {
  png(png_path, width = img_w * img_dpi, height = img_h * img_dpi,
      res = img_dpi, bg = "white")
}

plot_forest_stratification_meta_expanded2(
  dt               = dt_cog,
  terms            = terms_all,
  term_labels      = terms_rename,
  cohorts          = c("NACC", "AIBL", "HABS"),
  interaction_only = TRUE,  # Set to TRUE if you only want to plot the drug * time rows
  
  # Group tracking parameters for the 5 parallel blocks
  prog_groups      = c("Overall", "Non-progression", "CU-MCI progression", "CU/MCI-ADem progression", "ADem-stable"),
  group_colors     = c("#2F4F4F", "#BB9393", "#FEAD76", "#E64B35", "#756BB1"),
  
  # Custom x-axis window boundaries for each of your 5 clinical group columns
  xlim_cols        = list(
    `Overall`               = c(-0.05, 0.05),
    `Non-progression`       = c(-0.025, 0.025),
    `CU-MCI progression`    = c(-0.1, 0.2),
    `CU/MCI-AD progression` = c(-1, 1),
    `AD`                    = c(-1, 0.5)
  ),
  
  col_label_width  = 0.08,   # Space for left features/cohort labels
  forest_col_frac  = 0.48,   # 48% forest line graph / 52% text window ratio inside columns
  
  gap_feature      = 0.60,
  sub_row_h        = 0.55,
  cex_base         = 0.90,   # Sized perfectly for 5-column text spacing
  ci_lwd           = 2.4,
  point_cex        = 1.1,
  diamond_height   = 0.38,
  
  # title            = "Stratified Forest Plot – Cognitive Decline: Medication × Time Across Clinical Progression",
  title            = " ",
  show_legend      = TRUE,
  show_vline       = TRUE,
  mar              = c(6.5, 0.5, 5, 0.5)  # Extended bottom cushion prevents legend clipping
)

dev.off()
message("Saved: ", png_path)
```

