---
title: "Forest Plots - Main Analysis with Stratification"
author: "Yihan Wang"
date: "2025-09-16"
output: word_document
---

# Summary of Updates:
# 1. Added comorbidity adjustments (CVD, Endocrine, Psychiatric) to all models
# 2. Added age stratification (< 75 vs >= 75 years at baseline)
#    - Age is based on BASELINE age (participant-level, not record-level)
#    - This ensures consistent grouping across all visits for each participant
# 3. Maintained sex and APOE4 stratification
# 4. All models include medication × time interactions for longitudinal effects
#
# Stratification Summary:
# - Full cohort (no stratification)
# - By Sex: Female vs Male
# - By APOE4: Carriers vs Non-carriers
# - By Age: < 75 years vs >= 75 years (at baseline)
#
# Note on Drug-Drug Interactions:
# Adding all pairwise drug interactions would create 21 interaction terms (7 drugs choose 2).
# This is computationally expensive and may lead to overfitting. 
# Recommendations:
# - Focus on clinically relevant combinations (e.g., ACEi+ARB, Statin+Metformin)
# - Use data-driven approach: correlation analysis to identify common co-prescriptions
# - Consider three-way interactions with time for longitudinal effects
# See utility functions in medication-lmer-utility.R for drug combination analysis.

```{r}
rm(list=ls())
library(missRanger)
library(dplyr)
library(lubridate)
library(lme4)       # mixed models
library(lmerTest)   # p-values for lmer
library(splines)
library(conflicted)
library(broom.mixed)
library(dplyr)
library(stringr)
library(forcats)
library(ggplot2)
library(forestploter)
library(grid)
library(gridtext)
conflicts_prefer(dplyr::lag)
conflicts_prefer(lmerTest::lmer)
conflicts_prefer(dplyr::filter)
```

```{r}
source("medication-lmer-utility.R")
source("plots.R")
```

# Models
```{r}
NACC_full_df_cdr<-read.csv("../preprocessed_data/NACC/NACC_cdr_imputed_binary.csv")
AIBL_full_df_cdr<-read.csv("../preprocessed_data/AIBL/AIBL_cdr_imputed_binary.csv")
HABS_full_df_cdr<-read.csv("../preprocessed_data/HABSHD/HABSHD_cdr_imputed_binary.csv")

NACC_full_df_cdr$edu <- scale(NACC_full_df_cdr$edu)
NACC_full_df_cdr$age <- scale(NACC_full_df_cdr$age)
AIBL_full_df_cdr$edu <- scale(AIBL_full_df_cdr$edu)
AIBL_full_df_cdr$age <- scale(AIBL_full_df_cdr$age)
HABS_full_df_cdr$edu <- scale(HABS_full_df_cdr$edu)
HABS_full_df_cdr$age <- scale(HABS_full_df_cdr$age)
```

```{r}
med_cols <- c("ACEi","ARB","BetaBlk","CCB","Diuretic","Metformin","Statin")
med_cols_rename <-c("ACEi","ARBs","β-Blocker","CCBs","Diuretics","Statins","Metformin")
disease_cols <- c('CVD', 'Endocrine', 'Psychiatric')
interaction_terms <- c("Statin:BetaBlk", "Statin:ACEi", "Statin:ARB", "Statin:Diuretic", "Statin:CCB", "BetaBlk:Diuretic", "ACEi:Diuretic", "ARB:Diuretic")
```

```{r}
cohorts <- list(
  NACC = NACC_full_df_cdr,
  AIBL = AIBL_full_df_cdr,
  HABS = HABS_full_df_cdr
)

common_pairs <- get_common_drug_pairs(cohorts)

# Access per-cohort breakdown
attr(common_pairs, "record")
```

```{r}
NACC_full_df_cdr$visit_date <- as.Date(NACC_full_df_cdr$visit_date, format = "%Y-%m-%d")
fit_full_NACC <- lmer(
  CDR ~ year_since_baseline +
    age + sex + edu + APOE4 +
    CVD + Endocrine + Psychiatric +
    ACEi + ARB + BetaBlk + CCB + Diuretic + Metformin + Statin + 
    ACEi:year_since_baseline + ARB:year_since_baseline + BetaBlk:year_since_baseline +
    CCB:year_since_baseline + Diuretic:year_since_baseline + 
    Metformin:year_since_baseline + Statin:year_since_baseline +
    (1 + year_since_baseline | id),
  data = NACC_full_df_cdr
)
summary(fit_full_NACC)
```



### Full
```{r}
NACC_full_df_cdr$visit_date <- as.Date(NACC_full_df_cdr$visit_date, format = "%Y-%m-%d")
fit_full_NACC <- lmer(
  CDR ~ year_since_baseline +
    age + sex + edu + APOE4 +
    CVD + Endocrine + Psychiatric +
    ACEi + ARB + BetaBlk + CCB + Diuretic + Metformin + Statin + 
    ACEi:year_since_baseline + ARB:year_since_baseline + BetaBlk:year_since_baseline +
    CCB:year_since_baseline + Diuretic:year_since_baseline + 
    Metformin:year_since_baseline + Statin:year_since_baseline +
    (1 + year_since_baseline | id),
  data = NACC_full_df_cdr
)
summary(fit_full_NACC)
```

```{r}
p.adjust(coef(summary(fit_full_NACC))[,"Pr(>|t|)"], method="BH")
```

```{r}
AIBL_full_df_cdr$visit_date <- as.Date(AIBL_full_df_cdr$visit_date, format = "%Y-%m-%d")
fit_full_AIBL <- lmer(
  CDR ~ year_since_baseline +
    age + sex + edu + APOE4 +
    CVD + Endocrine + Psychiatric +
    ACEi + ARB + BetaBlk + CCB + Diuretic + Metformin + Statin + 
    ACEi:year_since_baseline + ARB:year_since_baseline + BetaBlk:year_since_baseline +
    CCB:year_since_baseline + Diuretic:year_since_baseline + 
    Metformin:year_since_baseline + Statin:year_since_baseline +
    (1 + year_since_baseline | id),
  data = AIBL_full_df_cdr
)
summary(fit_full_AIBL)
```

```{r}
p.adjust(coef(summary(fit_full_AIBL))[,"Pr(>|t|)"], method="BH")
```


```{r}
HABS_full_df_cdr$visit_date <- as.Date(HABS_full_df_cdr$visit_date, format = "%Y-%m-%d")
fit_full_HABS <- lmer(
  CDR ~ year_since_baseline +
    age + sex + edu + APOE4 +
    CVD + Endocrine + Psychiatric +
    ACEi + ARB + BetaBlk + CCB + Diuretic + Metformin + Statin + 
    ACEi:year_since_baseline + ARB:year_since_baseline + BetaBlk:year_since_baseline +
    CCB:year_since_baseline + Diuretic:year_since_baseline + 
    Metformin:year_since_baseline + Statin:year_since_baseline +
    (1 + year_since_baseline | id),
  data = HABS_full_df_cdr
)
summary(fit_full_HABS)
```

```{r}
p.adjust(coef(summary(fit_full_HABS))[,"Pr(>|t|)"], method="BH")
```

## Gender Stratification
```{r}
NACC_male = NACC_full_df_cdr[NACC_full_df_cdr$sex == 0, ]
NACC_female = NACC_full_df_cdr[NACC_full_df_cdr$sex == 1, ]
AIBL_male = AIBL_full_df_cdr[AIBL_full_df_cdr$sex == 0, ]
AIBL_female = AIBL_full_df_cdr[AIBL_full_df_cdr$sex == 1, ]
HABS_male = HABS_full_df_cdr[HABS_full_df_cdr$sex == 0, ]
HABS_female = HABS_full_df_cdr[HABS_full_df_cdr$sex == 1, ]
```

```{r}
NACC_female$visit_date <- as.Date(NACC_female$visit_date, format = "%Y-%m-%d")
fit_female_NACC <- lmer(
  CDR ~ year_since_baseline +
    age + edu + APOE4 +
    CVD + Endocrine + Psychiatric +
    ACEi + ARB + BetaBlk + CCB + Diuretic + Metformin + Statin + 
    ACEi:year_since_baseline + ARB:year_since_baseline + BetaBlk:year_since_baseline +
    CCB:year_since_baseline + Diuretic:year_since_baseline + 
    Metformin:year_since_baseline + Statin:year_since_baseline +
    (1 + year_since_baseline | id),
  data = NACC_female
)
summary(fit_female_NACC)
```
```{r}
p.adjust(coef(summary(fit_female_NACC))[,"Pr(>|t|)"], method="BH")
```

```{r}
NACC_male$visit_date <- as.Date(NACC_male$visit_date, format = "%Y-%m-%d")
fit_male_NACC <- lmer(
  CDR ~ year_since_baseline +
    age + edu + APOE4 +
    CVD + Endocrine + Psychiatric +
    ACEi + ARB + BetaBlk + CCB + Diuretic + Metformin + Statin + 
    ACEi:year_since_baseline + ARB:year_since_baseline + BetaBlk:year_since_baseline +
    CCB:year_since_baseline + Diuretic:year_since_baseline + 
    Metformin:year_since_baseline + Statin:year_since_baseline +
    (1 + year_since_baseline | id),
  data = NACC_male
)
summary(fit_male_NACC)
```

```{r}
p.adjust(coef(summary(fit_male_NACC))[,"Pr(>|t|)"], method="BH")
```

```{r}
AIBL_female$visit_date <- as.Date(AIBL_female$visit_date, format = "%Y-%m-%d")
fit_female_AIBL <- lmer(
  CDR ~ year_since_baseline +
    age + edu + APOE4 +
    CVD + Endocrine + Psychiatric +
    ACEi + ARB + BetaBlk + CCB + Diuretic + Metformin + Statin + 
    ACEi:year_since_baseline + ARB:year_since_baseline + BetaBlk:year_since_baseline +
    CCB:year_since_baseline + Diuretic:year_since_baseline + 
    Metformin:year_since_baseline + Statin:year_since_baseline +
    (1 + year_since_baseline | id),
  data = AIBL_female
)
summary(fit_female_AIBL)
```
```{r}
p.adjust(coef(summary(fit_female_AIBL))[,"Pr(>|t|)"], method="BH")
```

```{r}
AIBL_male$visit_date <- as.Date(AIBL_male$visit_date, format = "%Y-%m-%d")
fit_male_AIBL <- lmer(
  CDR ~ year_since_baseline +
    age + edu + APOE4 +
    CVD + Endocrine + Psychiatric +
    ACEi + ARB + BetaBlk + CCB + Diuretic +  Metformin + Statin +
    ACEi:year_since_baseline + ARB:year_since_baseline + BetaBlk:year_since_baseline +
    CCB:year_since_baseline + Diuretic:year_since_baseline + 
    Metformin:year_since_baseline + Statin:year_since_baseline +
    (1 + year_since_baseline | id),
  data = AIBL_male
)
summary(fit_male_AIBL)
```

```{r}
p.adjust(coef(summary(fit_male_AIBL))[,"Pr(>|t|)"], method="BH")
```

```{r}
HABS_female$visit_date <- as.Date(HABS_female$visit_date, format = "%Y-%m-%d")
fit_female_HABS <- lmer(
  CDR ~ year_since_baseline +
    age + edu + APOE4 +
    CVD + Endocrine + Psychiatric +
    ACEi + ARB + BetaBlk + CCB + Diuretic +  Metformin + Statin +
    ACEi:year_since_baseline + ARB:year_since_baseline + BetaBlk:year_since_baseline +
    CCB:year_since_baseline + Diuretic:year_since_baseline + 
    Metformin:year_since_baseline + Statin:year_since_baseline +
    (1 + year_since_baseline | id),
  data = HABS_female
)
summary(fit_female_HABS)
```

```{r}
p.adjust(coef(summary(fit_female_HABS))[,"Pr(>|t|)"], method="BH")
```

```{r}
HABS_male$visit_date <- as.Date(HABS_male$visit_date, format = "%Y-%m-%d")
fit_male_HABS <- lmer(
  CDR ~ year_since_baseline +
    age + edu + APOE4 +
    CVD + Endocrine + Psychiatric +
    ACEi + ARB + BetaBlk + CCB + Diuretic + Metformin + Statin + 
    ACEi:year_since_baseline + ARB:year_since_baseline + BetaBlk:year_since_baseline +
    CCB:year_since_baseline + Diuretic:year_since_baseline + 
    Metformin:year_since_baseline + Statin:year_since_baseline +
    (1 + year_since_baseline | id),
  data = HABS_male
)
summary(fit_male_HABS)
```

```{r}
p.adjust(coef(summary(fit_male_HABS))[,"Pr(>|t|)"], method="BH")
```

## APOE Stratification
```{r}
NACC_APOEY = NACC_full_df_cdr[NACC_full_df_cdr$APOE4 == 1, ]
NACC_APOEN = NACC_full_df_cdr[NACC_full_df_cdr$APOE4 == 0, ]
AIBL_APOEY = AIBL_full_df_cdr[AIBL_full_df_cdr$APOE4 == 1, ]
AIBL_APOEN = AIBL_full_df_cdr[AIBL_full_df_cdr$APOE4 == 0, ]
HABS_APOEY = HABS_full_df_cdr[HABS_full_df_cdr$APOE4 == 1, ]
HABS_APOEN = HABS_full_df_cdr[HABS_full_df_cdr$APOE4 == 0, ]
```

```{r}
NACC_APOEY$visit_date <- as.Date(NACC_APOEY$visit_date, format = "%Y-%m-%d")
fit_APOEY_NACC <- lmer(
  CDR ~ year_since_baseline +
    age + sex + edu +
    CVD + Endocrine + Psychiatric +
    ACEi + ARB + BetaBlk + CCB + Diuretic + Metformin + Statin + 
    ACEi:year_since_baseline + ARB:year_since_baseline + BetaBlk:year_since_baseline +
    CCB:year_since_baseline + Diuretic:year_since_baseline + 
    Metformin:year_since_baseline + Statin:year_since_baseline +
    (1 + year_since_baseline | id),
  data = NACC_APOEY
)
summary(fit_APOEY_NACC)
```

```{r}
p.adjust(coef(summary(fit_APOEY_NACC))[,"Pr(>|t|)"], method="BH")
```

```{r}
NACC_APOEN$visit_date <- as.Date(NACC_APOEN$visit_date, format = "%Y-%m-%d")
fit_APOEN_NACC <- lmer(
  CDR ~ year_since_baseline +
    age + sex + edu +
    CVD + Endocrine + Psychiatric +
    ACEi + ARB + BetaBlk + CCB + Diuretic + Metformin + Statin + 
    ACEi:year_since_baseline + ARB:year_since_baseline + BetaBlk:year_since_baseline +
    CCB:year_since_baseline + Diuretic:year_since_baseline + 
    Metformin:year_since_baseline + Statin:year_since_baseline +
    (1 + year_since_baseline | id),
  data = NACC_APOEN
)
summary(fit_APOEN_NACC)
```

```{r}
p.adjust(coef(summary(fit_APOEN_NACC))[,"Pr(>|t|)"], method="BH")
```

```{r}
AIBL_APOEY$visit_date <- as.Date(AIBL_APOEY$visit_date, format = "%Y-%m-%d")
fit_APOEY_AIBL <- lmer(
  CDR ~ year_since_baseline +
    age + sex + edu +
    CVD + Endocrine + Psychiatric +
    ACEi + ARB + BetaBlk + CCB + Diuretic + Metformin + Statin + 
    ACEi:year_since_baseline + ARB:year_since_baseline + BetaBlk:year_since_baseline +
    CCB:year_since_baseline + Diuretic:year_since_baseline + 
    Metformin:year_since_baseline + Statin:year_since_baseline +
    (1 + year_since_baseline | id),
  data = AIBL_APOEY
)
summary(fit_APOEY_AIBL)
```

```{r}
p.adjust(coef(summary(fit_APOEY_AIBL))[,"Pr(>|t|)"], method="BH")
```

```{r}
AIBL_APOEN$visit_date <- as.Date(AIBL_APOEN$visit_date, format = "%Y-%m-%d")
fit_APOEN_AIBL <- lmer(
  CDR ~ year_since_baseline +
    age + sex + edu +
    CVD + Endocrine + Psychiatric +
    ACEi + ARB + BetaBlk + CCB + Diuretic + Metformin + Statin + 
    ACEi:year_since_baseline + ARB:year_since_baseline + BetaBlk:year_since_baseline +
    CCB:year_since_baseline + Diuretic:year_since_baseline + 
    Metformin:year_since_baseline + Statin:year_since_baseline +
    (1 + year_since_baseline | id),
  data = AIBL_APOEN
)
summary(fit_APOEN_AIBL)
```

```{r}
p.adjust(coef(summary(fit_APOEN_AIBL))[,"Pr(>|t|)"], method="BH")
```

```{r}
HABS_APOEY$visit_date <- as.Date(HABS_APOEY$visit_date, format = "%Y-%m-%d")
fit_APOEY_HABS <- lmer(
  CDR ~ year_since_baseline +
    age + sex + edu +
    CVD + Endocrine + Psychiatric +
    ACEi + ARB + BetaBlk + CCB + Diuretic + Metformin + Statin + 
    ACEi:year_since_baseline + ARB:year_since_baseline + BetaBlk:year_since_baseline +
    CCB:year_since_baseline + Diuretic:year_since_baseline + 
    Metformin:year_since_baseline + Statin:year_since_baseline +
    (1 + year_since_baseline | id),
  data = HABS_APOEY
)
summary(fit_APOEY_HABS)
```
```{r}
p.adjust(coef(summary(fit_APOEY_HABS))[,"Pr(>|t|)"], method="BH")
```

```{r}
HABS_APOEN$visit_date <- as.Date(HABS_APOEN$visit_date, format = "%Y-%m-%d")
fit_APOEN_HABS <- lmer(
  CDR ~ year_since_baseline +
    age + sex + edu +
    CVD + Endocrine + Psychiatric +
    ACEi + ARB + BetaBlk + CCB + Diuretic + Metformin + Statin + 
    ACEi:year_since_baseline + ARB:year_since_baseline + BetaBlk:year_since_baseline +
    CCB:year_since_baseline + Diuretic:year_since_baseline + 
    Metformin:year_since_baseline + Statin:year_since_baseline +
    (1 + year_since_baseline | id),
  data = HABS_APOEN
)
summary(fit_APOEN_HABS)
```

```{r}
p.adjust(coef(summary(fit_APOEN_HABS))[,"Pr(>|t|)"], method="BH")
```

## Age Stratification (baseline age)
```{r}
# Get baseline age for each participant
get_baseline_age <- function(df) {
  df %>%
    group_by(id) %>%
    filter(visit_no == 1) %>%
    select(id, age) %>%
    ungroup()
}
NACC_full_df_cdr<-read.csv("../preprocessed_data/NACC/NACC_cdr_imputed_binary.csv")
AIBL_full_df_cdr<-read.csv("../preprocessed_data/AIBL/AIBL_cdr_imputed_binary.csv")
HABS_full_df_cdr<-read.csv("../preprocessed_data/HABSHD/HABSHD_cdr_imputed_binary.csv")

# Create age groups based on baseline age
NACC_baseline_age <- get_baseline_age(NACC_full_df_cdr)
AIBL_baseline_age <- get_baseline_age(AIBL_full_df_cdr)
HABS_baseline_age <- get_baseline_age(HABS_full_df_cdr)

# Merge back and create age groups
NACC_full_df_cdr <- NACC_full_df_cdr %>%
  select(-age) %>%
  left_join(NACC_baseline_age, by = "id") %>%
  mutate(age_group = ifelse(age < 75, "Age < 75", "Age >= 75"))

AIBL_full_df_cdr <- AIBL_full_df_cdr %>%
  select(-age) %>%
  left_join(AIBL_baseline_age, by = "id") %>%
  mutate(age_group = ifelse(age < 75, "Age < 75", "Age >= 75"))

HABS_full_df_cdr <- HABS_full_df_cdr %>%
  select(-age) %>%
  left_join(HABS_baseline_age, by = "id") %>%
  mutate(age_group = ifelse(age < 75, "Age < 75", "Age >= 75"))

# Split by age groups
NACC_age_young = NACC_full_df_cdr[NACC_full_df_cdr$age_group == "Age < 75", ]
NACC_age_old = NACC_full_df_cdr[NACC_full_df_cdr$age_group == "Age >= 75", ]
AIBL_age_young = AIBL_full_df_cdr[AIBL_full_df_cdr$age_group == "Age < 75", ]
AIBL_age_old = AIBL_full_df_cdr[AIBL_full_df_cdr$age_group == "Age >= 75", ]
HABS_age_young = HABS_full_df_cdr[HABS_full_df_cdr$age_group == "Age < 75", ]
HABS_age_old = HABS_full_df_cdr[HABS_full_df_cdr$age_group == "Age >= 75", ]
```

```{r}
NACC_age_young$visit_date <- as.Date(NACC_age_young$visit_date, format = "%Y-%m-%d")
fit_age_young_NACC <- lmer(
  CDR ~ year_since_baseline +
    age + sex + edu + APOE4 +
    CVD + Endocrine + Psychiatric +
    ACEi + ARB + BetaBlk + CCB + Diuretic + Metformin + Statin + 
    ACEi:year_since_baseline + ARB:year_since_baseline + BetaBlk:year_since_baseline +
    CCB:year_since_baseline + Diuretic:year_since_baseline + 
    Metformin:year_since_baseline + Statin:year_since_baseline +
    (1 + year_since_baseline | id),
  data = NACC_age_young
)
summary(fit_age_young_NACC)
```

```{r}
p.adjust(coef(summary(fit_age_young_NACC))[,"Pr(>|t|)"], method="BH")
```

```{r}
NACC_age_old$visit_date <- as.Date(NACC_age_old$visit_date, format = "%Y-%m-%d")
fit_age_old_NACC <- lmer(
  CDR ~ year_since_baseline +
    age + sex + edu + APOE4 +
    CVD + Endocrine + Psychiatric +
    ACEi + ARB + BetaBlk + CCB + Diuretic + Metformin + Statin + 
    ACEi:year_since_baseline + ARB:year_since_baseline + BetaBlk:year_since_baseline +
    CCB:year_since_baseline + Diuretic:year_since_baseline + 
    Metformin:year_since_baseline + Statin:year_since_baseline +
    (1 + year_since_baseline | id),
  data = NACC_age_old
)
summary(fit_age_old_NACC)
```

```{r}
p.adjust(coef(summary(fit_age_old_NACC))[,"Pr(>|t|)"], method="BH")
```

```{r}
AIBL_age_young$visit_date <- as.Date(AIBL_age_young$visit_date, format = "%Y-%m-%d")
fit_age_young_AIBL <- lmer(
  CDR ~ year_since_baseline +
    age + sex + edu + APOE4 +
    CVD + Endocrine + Psychiatric +
    ACEi + ARB + BetaBlk + CCB + Diuretic + Metformin + Statin + 
    ACEi:year_since_baseline + ARB:year_since_baseline + BetaBlk:year_since_baseline +
    CCB:year_since_baseline + Diuretic:year_since_baseline + 
    Metformin:year_since_baseline + Statin:year_since_baseline +
    (1 + year_since_baseline | id),
  data = AIBL_age_young
)
summary(fit_age_young_AIBL)
```

```{r}
p.adjust(coef(summary(fit_age_young_AIBL))[,"Pr(>|t|)"], method="BH")
```

```{r}
AIBL_age_old$visit_date <- as.Date(AIBL_age_old$visit_date, format = "%Y-%m-%d")
fit_age_old_AIBL <- lmer(
  CDR ~ year_since_baseline +
    age + sex + edu + APOE4 +
    CVD + Endocrine + Psychiatric +
    ACEi + ARB + BetaBlk + CCB + Diuretic + Metformin + Statin + 
    ACEi:year_since_baseline + ARB:year_since_baseline + BetaBlk:year_since_baseline +
    CCB:year_since_baseline + Diuretic:year_since_baseline + 
    Metformin:year_since_baseline + Statin:year_since_baseline +
    (1 + year_since_baseline | id),
  data = AIBL_age_old
)
summary(fit_age_old_AIBL)
```

```{r}
p.adjust(coef(summary(fit_age_old_AIBL))[,"Pr(>|t|)"], method="BH")
```

```{r}
HABS_age_young$visit_date <- as.Date(HABS_age_young$visit_date, format = "%Y-%m-%d")
fit_age_young_HABS <- lmer(
  CDR ~ year_since_baseline +
    age + sex + edu + APOE4 +
    CVD + Endocrine + Psychiatric +
    ACEi + ARB + BetaBlk + CCB + Diuretic + Metformin + Statin + 
    ACEi:year_since_baseline + ARB:year_since_baseline + BetaBlk:year_since_baseline +
    CCB:year_since_baseline + Diuretic:year_since_baseline + 
    Metformin:year_since_baseline + Statin:year_since_baseline +
    (1 + year_since_baseline | id),
  data = HABS_age_young
)
summary(fit_age_young_HABS)
```

```{r}
p.adjust(coef(summary(fit_age_young_HABS))[,"Pr(>|t|)"], method="BH")
```

```{r}
HABS_age_old$visit_date <- as.Date(HABS_age_old$visit_date, format = "%Y-%m-%d")
fit_age_old_HABS <- lmer(
  CDR ~ year_since_baseline +
    age + sex + edu + APOE4 +
    CVD + Endocrine + Psychiatric +
    ACEi + ARB + BetaBlk + CCB + Diuretic + Metformin + Statin + 
    ACEi:year_since_baseline + ARB:year_since_baseline + BetaBlk:year_since_baseline +
    CCB:year_since_baseline + Diuretic:year_since_baseline + 
    Metformin:year_since_baseline + Statin:year_since_baseline +
    (1 + year_since_baseline | id),
  data = HABS_age_old
)
summary(fit_age_old_HABS)
```

```{r}
p.adjust(coef(summary(fit_age_old_HABS))[,"Pr(>|t|)"], method="BH")
```





# plots
```{r}
terms_all <-c(
    "year_since_baseline","age","sex","edu","APOE4",
    "CVD", "Endocrine", "Psychiatric",
    "ACEi","ARB","BetaBlk","CCB",
    "Diuretic","Metformin", "Statin",
    "year_since_baseline:ACEi","year_since_baseline:ARB",
    "year_since_baseline:BetaBlk","year_since_baseline:CCB",
    "year_since_baseline:Diuretic", "year_since_baseline:Metformin",
    "year_since_baseline:Statin"
  )
terms_rename <- c(
    "year_since_baseline"="Time",
    "age"="Age (baseline)",
    "sex"="Sex (ref: Male)",
    "edu"="Education (z-scored)",
    "APOE4"="APOE4 carrier (ref: No)",
    "CVD"="CVD",
    "Endocrine"="Endocrine disease",
    "Psychiatric"="Psychiatric disease",
    "ACEi"="ACEi",
    "ARB"="ARBs",
    "BetaBlk"="β-Blocker",
    "CCB"="CCBs",
    "Diuretic"="Diuretics",
    "Metformin"="Metformin",
    "Statin"="Statins",
    "year_since_baseline:ACEi"="ACEi × Time",
    "year_since_baseline:ARB"="ARBs × Time",
    "year_since_baseline:BetaBlk"="β-Blocker × Time",
    "year_since_baseline:CCB"="CCBs × Time",
    "year_since_baseline:Diuretic"="Diuretics × Time",
    "year_since_baseline:Metformin"="Metformin × Time",
    "year_since_baseline:Statin"="Statins × Time"
  )
```

## old version
```{r}
# plot_forest_subset_meta_expanded(
#   fits = list(
#     Full     = list(fit_full_NACC,   fit_full_AIBL,   fit_full_HABS),
#     Female   = list(fit_female_NACC, fit_female_AIBL, fit_female_HABS),
#     Male     = list(fit_male_NACC,   fit_male_AIBL,   fit_male_HABS),
#     `APOE4 carriers`     = list(fit_APOEY_NACC,  fit_APOEY_AIBL,  fit_APOEY_HABS),
#     `APOE4 non-carriers` = list(fit_APOEN_NACC,  fit_APOEN_AIBL,  fit_APOEN_HABS),
#     `Age < 75` = list(fit_age_young_NACC, fit_age_young_AIBL, fit_age_young_HABS),
#     `Age >= 75` = list(fit_age_old_NACC, fit_age_old_AIBL, fit_age_old_HABS)
#   ),
#   terms         = terms_all,
#   groups        = c("Full","Female","Male","APOE4 carriers","APOE4 non-carriers","Age < 75","Age >= 75"),
#   cohorts       = c("NACC","AIBL","HABS-HD"),
#   term_labels   = terms_rename,
#   title         = "",
#   filename      = "../plots/forestplot/CDR_forestplot_main_baseline.pdf",
#   width         = 35, height = 12,
#   ref_line      = 0,
#   # xlim_fixed    = c(-0.8, 0.8),
#   xlim_per_group = list(
#   Full = c(-0.4, 0.4),
#   Female = c(-0.5, 0.5),
#   Male = c(-0.5, 0.5),
#   "APOE4 carriers" = c(-0.5, 0.5),
#   "APOE4 non-carriers" = c(-0.4, 0.4),
#   "Age < 75" = c(-0.4, 0.4),
#   "Age >= 75" = c(-0.5, 0.5)
# ),
#   cohort_colors = c("#DAA87C", "#92A5D1", "#C9DCC4"),
#   cohort_shapes = c(15, 16, 18),
#   IF_META_ANALYSIS = TRUE, meta_label = "Meta", meta_color = "#fe6666", meta_shape = 17,
#   row_padding_mm = 6, lineheight_txt = 0.05,
#   point_size = 0.8, line_width = 2.8,
#   # ABSOLUTE widths in INCHES (not fractions!)
#   add_gutter = TRUE,gutter_width=0.10,
#   # gutter_width = 0.2,       # 0.5 inches between groups
#   first_col_width = 3.5,    # 3.5 inches for Measurements
#   est_frac = 3.0,           # 2.5 inches for Estimate (SE)
#   wgt_frac = 2.0,           # 1.5 inches for Weight
#   ci_frac = 8.0,            # 8 inches for CI plot (WIDE!)
#   block_col1 = "#f8f1ff", block_col2 = "#FFFFFF",
#   p_adjust = 'BH',
#   feature_subset=c("ACEi","ARB","BetaBlk","CCB","Diuretic","Metformin", "Statin")
# )
```

```{r}
# plot_forest_subset_meta_expanded(
#   fits = list(
#     Full     = list(fit_full_NACC,   fit_full_AIBL,   fit_full_HABS),
#     Female   = list(fit_female_NACC, fit_female_AIBL, fit_female_HABS),
#     Male     = list(fit_male_NACC,   fit_male_AIBL,   fit_male_HABS),
#     `APOE4 carriers`     = list(fit_APOEY_NACC,  fit_APOEY_AIBL,  fit_APOEY_HABS),
#     `APOE4 non-carriers` = list(fit_APOEN_NACC,  fit_APOEN_AIBL,  fit_APOEN_HABS),
#     `Age < 75` = list(fit_age_young_NACC, fit_age_young_AIBL, fit_age_young_HABS),
#     `Age >= 75` = list(fit_age_old_NACC, fit_age_old_AIBL, fit_age_old_HABS)
#   ),
#   terms         = terms_all,
#   groups        = c("Full","Female","Male","APOE4 carriers","APOE4 non-carriers","Age < 75","Age >= 75"),
#   cohorts       = c("NACC","AIBL","HABS-HD"),
#   term_labels   = terms_rename,
#   title         = "",
#   filename      = "../plots/forestplot/CDR_forestplot_main_longitudinal.pdf",
#   width         = 35, height = 12,
#   ref_line      = 0,
#   # xlim_fixed    = c(-0.2, 0.2),
#   xlim_per_group = list(
#   Full = c(-0.1, 0.1),
#   Female = c(-0.1, 0.1),
#   Male = c(-0.1, 0.1),
#   "APOE4 carriers" = c(-0.1, 0.1),
#   "APOE4 non-carriers" = c(-0.1, 0.1),
#   "Age < 75" = c(-0.1, 0.1),
#   "Age >= 75" = c(-0.1, 0.1)
# ),
#   cohort_colors = c("#DAA87C", "#92A5D1", "#C9DCC4"),
#   cohort_shapes = c(15, 16, 18),
#   IF_META_ANALYSIS = TRUE, meta_label = "Meta", meta_color = "#fe6666", meta_shape = 17,
#   row_padding_mm = 6, lineheight_txt = 0.05,
#   point_size = 0.85, line_width = 2.8,
#   # ABSOLUTE widths in INCHES (not fractions!)
#   add_gutter = TRUE,gutter_width=0.10,
#   # gutter_width = 0.2,       # 0.5 inches between groups
#   first_col_width = 3.5,    # 3.5 inches for Measurements
#   est_frac = 3.0,           # 2.5 inches for Estimate (SE)
#   wgt_frac = 2.0,           # 1.5 inches for Weight
#   ci_frac = 8.0,            # 8 inches for CI plot (WIDE!)
#   block_col1 = "#f8f1ff", block_col2 = "#FFFFFF",
#   p_adjust = 'BH',
#   feature_subset=c("year_since_baseline:ACEi","year_since_baseline:ARB",
#     "year_since_baseline:BetaBlk","year_since_baseline:CCB",
#     "year_since_baseline:Diuretic", "year_since_baseline:Metformin",
#     "year_since_baseline:Statin")
# )
```

```{r}
# dt_ = make_dt_from_fits(
#   fits = list(
#     Full     = list(fit_full_NACC,   fit_full_AIBL,   fit_full_HABS),
#     Female   = list(fit_female_NACC, fit_female_AIBL, fit_female_HABS),
#     Male     = list(fit_male_NACC,   fit_male_AIBL,   fit_male_HABS),
#     `APOE4 carriers` = list(fit_APOEY_NACC,  fit_APOEY_AIBL,  fit_APOEY_HABS),
#     `APOE4 non-carriers` = list(fit_APOEN_NACC,  fit_APOEN_AIBL,  fit_APOEN_HABS),
#     `Age < 75` = list(fit_age_young_NACC, fit_age_young_AIBL, fit_age_young_HABS),
#     `Age >= 75` = list(fit_age_old_NACC, fit_age_old_AIBL, fit_age_old_HABS)
#   ),
#   term= terms_all,
#   cohorts = c("NACC","AIBL","HABS"),
#   term_labels  = terms_rename,
#   method = "REML",
#   digits = 3, 
#   p_adjust = "BH"
# )
```

```{r}
dt_t = make_dt_from_fits(
  fits = list(
    Full     = list(fit_full_NACC,   fit_full_AIBL,   fit_full_HABS),
    Female   = list(fit_female_NACC, fit_female_AIBL, fit_female_HABS),
    Male     = list(fit_male_NACC,   fit_male_AIBL,   fit_male_HABS),
    `APOE4 carriers` = list(fit_APOEY_NACC,  fit_APOEY_AIBL,  fit_APOEY_HABS),
    `APOE4 non-carriers` = list(fit_APOEN_NACC,  fit_APOEN_AIBL,  fit_APOEN_HABS),
    `Age < 75` = list(fit_age_young_NACC, fit_age_young_AIBL, fit_age_young_HABS),
    `Age >= 75` = list(fit_age_old_NACC, fit_age_old_AIBL, fit_age_old_HABS)
  ),
  term= terms_all,
  cohorts = c("NACC","AIBL","HABS"),
  term_labels  = terms_rename,
  method = "REML",
  digits = 3, 
  p_adjust = "none"
)
```

## Stratified Forest Plot (Gender, APOE4, Age)
```{r forest-strat, fig.width=20, fig.height=15, dev="png", dpi=1200}
# ── Save as PNG (avoids PDF Unicode issues with β, ×, –, etc.) ───────────────
# ragg::agg_png() gives the best font rendering; falls back to plain png().
png_path <- "../plots/forestplot/Figure 3.png"
dir.create(dirname(png_path), recursive = TRUE, showWarnings = FALSE)

# Width/height in pixels: inches × dpi
img_w <- 10; img_h <- 15; img_dpi <- 900

if (requireNamespace("ragg", quietly = TRUE)){
  ragg::agg_png(png_path, width = img_w, height = img_h,
                units = "in", res = img_dpi, background = "white")
} else {
  png(png_path, width = img_w * img_dpi, height = img_h * img_dpi,
      res = img_dpi, bg = "white")
}

plot_forest_stratification_meta_expanded(
  dt          = dt_t,
  terms       = terms_all,
  term_labels = terms_rename,
  cohorts     = c("NACC", "AIBL", "HABS"),

  interaction_only = TRUE,

  strat_pairs = list(
    "Gender" = c("Female",          "Male"),
    "APOE4"  = c("APOE4 carriers",  "APOE4 non-carriers"),
    "Age"    = c("Age < 75",         "Age >= 75")
  ),

  colors_A = c("#E64B35", "#238B45", "#BB9393"),
  colors_B = c("#3182BD", "#756BB1", "#808080"),

  xlim_cols = list(
    Gender = c(-0.15, 0.1),
    APOE4  = c(-0.15, 0.1),
    Age    = c(-0.25, 0.2)
  ),

  col_label_width = 0.1,   # narrow left label
  forest_col_frac = 0.5,   # forest = 42% of each column; text fills the rest
  col_gap_frac    = 0.05,  # tiny gap between columns

  gap_pair       = 0,
  gap_meta       = 0,
  gap_feature    = 0.60,
  sub_row_h      = 0.55,
  cex_base       = 0.95,
  ci_lwd         = 2.4,
  point_cex      = 1.1,
  diamond_height = 0.38,

  # title       = "Stratified Forest Plot \u2013 CDR: Medication \u00d7 Time",
  title       = " ",
  show_legend = TRUE,
  show_vline  = TRUE,
  mar         = c(4, 0.5, 5, 0.5)
)

dev.off()
message("Saved: ", png_path)
```

